Responses to Reviewer Three

### 2021-05-11 Scripts/Reviews/reviewer_one.Rmd
All responses done
Initial round of revisions done

---
title: "Response to Reviewer One"
output: pdf_document
---

- Response: [Not responded] 
- *Response*: [Draft response here] 
- **Response**: [Response completed her and in manuscript]

@@

- Response: Thank you very much for commenting on our figures. Here, we provide responses to the two large scale questions you provide and below we respond the finer scale points. We hope that this clarifies all of your comments.

 - **Regarding the bi-lateral agreements**, this is a great question that, unfortunately, we cannot respond at this moment. Currently, there is only one database on bi-lateral agreements produce by Oremus *et al* (2020). On their paper, the authors state "we analysed 27 publicly available international fisheries agreements in the South Pacific, Southeast Asia, South Asia, Northwest Africa, and Central America and the Caribbean" and " For each agreement, we recorded the following information... If relevant, to which specific stock or species the agreement pertained". However, the authors do not provide any information at the stock level and, unfortunately, they never respond/ did not shared their database with us.

We hope that the reviewer understands the complexity of building such database and that this exercise falls outside the scope and stage of our current analysis. We agree that having such information would increase the manuscript impact, but, would not necessarily directly impact our results nor the message we want to covein (Ultimately oremus *et at* state it very clearly in their paper, "None of the 127 agreements contains language that is directly related to climate change, range shifts or stock exits").

Oremus KL, Bone J, Costello C, Molinos JG, Lee A, Mangin T, Salzman J. 2020. Governance challenges for tropical nations losing fish species due to climate change. Nature Sustainability 6:1–4. Nature Publishing Group. Available from https://www.nature.com/articles/s41893-020-0476-y.

 - **Regarding model-specific variance.** For this paper we used one climate model (the GFDL) forced following one climate change scenario (RCP 8.5) to couple with one species distribution model. For this reason, providing quantitative upper and lower bounds of our results is not possible and would require substantial extra computation. However, because we have 10 different runs of the GFDL and employ the time of emergence concept, we are capable of providing a less conservative estimate of the numbers you mention (i.e., the number of shifting stocks and EEZs). This was originally presented in the methods section as a sensitivity analysis and has now been moved to the Methods section of the main paper (**NOTE TO CO-AUTHORS**: Should we include this in the results?). It reads on line *XXX* of page *XX*: *We also computed a less conservative estimation of shifting transboundary stocks by including a threshold of one standard deviation (i.e., representing a probability of 68% that the stock had shifted from natural variation; see methods). In this case, the global average shift in the shared distribution of transboundary stocks is 2029 $\pm$ 27 years, a difference of about 7 years (Fig. S8). In total, 5,745 transboundary stocks would shift their shared distributions between 2006 and 2100 considering a less conservative metric, that is, 33% (n = 1626) more shifting stocks (Figs. S2 and S8).*

@@

- **Response:** Thank you for this comment. We have eddited the paragraph starting at line **13** of page **12** to reflect this comment.

>>>>

---
title: "Response to Reviewer One"
# output: pdf_document
output: word_document
---

@@

- **Response:** Thank you very much for commenting on our figures. Here, we provide responses to the two large scale questions you provide and below we respond the finer scale points. We hope that this clarifies all of your comments.

 - **Regarding the bi-lateral agreements**, this is a great question that, unfortunately, we cannot respond at this moment. Currently, there is only one database on bi-lateral agreements produce by Oremus *et al* (2020). On their paper, the authors state "we analysed 127 publicly available international fisheries agreements in the South Pacific, Southeast Asia, South Asia, Northwest Africa, and Central America and the Caribbean" and " For each agreement, we recorded the following information... If relevant, to which specific stock or species the agreement pertained". We contacted Dr. (Kimberly) Oremus who provided the provided the mentioned dataset. However, non of the 127 treaties have identified subjects at the species level (except for bigeye, skipjack and yellowtail tunas).

We hope that the reviewer understands the complexity of building such database and that this exercise falls outside the scope and stage of our current analysis. We agree that having such information would increase the manuscript impact, but, would not necessarily directly impact our results nor the message we want to covein (Ultimately Oremus *et at* state it very clearly in their paper, "None of the 127 agreements contains language that is directly related to climate change, range shifts or stock exits").

 - Oremus KL, Bone J, Costello C, Molinos JG, Lee A, Mangin T, Salzman J. 2020. Governance challenges for tropical nations losing fish species due to climate change. Nature Sustainability 6:1–4. Nature Publishing Group.

 - **Regarding model-specific variance.** For this paper we used one climate model (the GFDL) forced following one climate change scenario (RCP 8.5) to couple with one species distribution model. For this reason, providing quantitative upper and lower bounds of our results is not possible and would require substantial extra computation. However, because we have 10 different runs of the GFDL and employ the time of emergence concept, we are capable of providing a less conservative estimate of the numbers you mention (i.e., the number of shifting stocks and EEZs). This was originally presented in the methods section as a sensitivity analysis and has now been moved to the Methods section of the main paper (**NOTE TO CO-AUTHORS**: Should we include this in the results or leave it in the methods?). It reads on line *XXX* of page *XX*: *We also computed a less conservative estimation of shifting transboundary stocks by including a threshold of one standard deviation (i.e., representing a probability of 68% that the stock had shifted from natural variation; see methods). In this case, the global average shift in the shared distribution of transboundary stocks is 2029 $\pm$ 27 years, a difference of about 7 years (Fig. S8). In total, 5,745 transboundary stocks would shift their shared distributions between 2006 and 2100 considering a less conservative metric, that is, 33% (n = 1626) more shifting stocks (Figs. S2 and S8).*

@@

- **Response:** Thank you for this comment. We have edited the paragraph starting at line **13** of page **12** to reflect this comment.

### 2021-05-11 Scripts/Reviews/reviewer_three.Rmd
Initial round of revisions done

---
title: "Responses to Reviewer Three"
output: pdf_document
---

- Response: [Not responded] 
- *Response*: [Draft response here] 
- **Response**: [Response compleded her and in manuscript]

@@

- Informing global fisheries sustainability and meeting the SDG 2030 Agenda is a useful framing, in my opinion. However, given that framing and the research questions posed in this paper, I think the authors have overlooked two very important cases: 1) stocks that are currently confined to a single EEZ (“national stocks”) that will shift into transboundary stocks by 2100, and 2) stocks that are currently transboundary stocks that will shift entirel into a single EEZ by 2100, becoming national stocks. From a sustainability perspective, I am more concerned about case #1 than stocks that are already transboundary that are going to shift their distributions but maintain their transboundary status (the only cases currently examined in this paper). Some of those stocks might already have cooperative management agreements in place. And if they don’t, they are already plagued by the overharvesting that is likely to occur in the absence of international cooperation. Stocks that are currently national, however, have a higher likelihood of being managed sustainably now, and that likelihood will decline when they become transboundary. This seems like the most important case to analyze, and one that seems totally feasible to examine within the authors’ analysis framework, and yet this seems to have been completely overlooked. I also think it would be interesting to determine what proportion of current transboundary stocks become national stocks – the authors should have been able to detect these cases and I would assume there are some, but it is not mentioned anywhere in the paper. This seems like a missed opportunity for greater insights and is a mismatch between the stated goals of the paper and the results that are presented.

@@

 - Pg 9, Line 6: is 59% the proportion of stocks that will shift their catch distribution? Or is it the average proportion of the catch that shifts between countries?

@@

- The methods are ENTIRELY in the supplementary materials. I have no problem with more abbreviated methods in the main paper and more details in the supplement, but there needs to be some methods in the main paper. A reader needs to be able to understand the basic approach without going to the supplementary materials.

@@

- Pg 31-32: Does the TI capture the equality of sharing of the stock between two countries, or just how stable it is over time? The text claims an increasing TI means management is getting more challenging and a decreasing TI that the sharing between countries is becoming more stable (but not necessarily more equal)….is that the right interpretation? And how does that align with the example in Fig S6, where the TI seems to decline over the entire time series…..does that mean the sharing is becoming more stable?

*Response:* Thank you for your comment. The transboundary index only captures the sharing stability over time. We had originally explored the directionality of the TI per stock, however, this was removed from the analysis as we rather focused on the "time of emergence" of the future TI from historical variability. Thus, since we do not talk about the directionallity of the TI (nor the TI *per se*) we have removed this sentence to avoid misunderstanding.

The equality of sharing is measured by the Stock Share Ratio described under *Quantifying the intensity of transboundary stocks’ range shift.*

- I like the time of emergence concept and how it was applied in this analysis.

**Response:** We appreciate the acknowledgment on our methods.

- I also like the idea of the threat point analysis to identify when a stock is sufficiently shared with another country to motivate cooperative management. However, I was confused by how the threat point was implemented using the stock share ratio (SSR) – why is the threat point determined relative to the historic SSR? I assume the idea of a threat point from game theory is based on the proportion of catch or value that is shared, and I don’t see how the starting point SSR would be relevant? Maybe I misunderstood what the authors did here, but conceptually/theoretically I’m not understanding the rationale for their approach so at the very least it needs more explanation and justification. But I’m concerned it actually needs to be based on a theoretical proportion, not a quantity interpreted relative to a historic proportion.

- Response: Missing

- I think a version of Fig. S6 would be useful for the main paper. (But a few small comments about this figure: in panel a, I don’t understand why the EEZ centroids aren’t shown in the middle of the EEZ boxes? Also, for panel b, I see a red open circle in the legend, but I don’t see that anywhere on the actual figure.)

**Response:** Thank you for noticing the misplace of the EEZ centroids. The figure has been corrected and included the figure in the main text (It is now Fig. 1). The open red circles are located in the bottom panel (B) in each time step where the future distribution overpasses the natural variability.

@@

- I know this is nitpicky, but please don’t have line numbers restart on each page. It just makes it more cumbersome on a reviewer trying to give detailed comments.

**Response:** We understand (and agree!) with this comment. Unfortunately, this is how the *Science* template was distributed to us.

- Page1, Line 15: I suggest reporting the proportion of stocks (which looks like it would be between 20-25%), rather than the 78% reported here. Saying that transboundary stocks will shift their distributions across 78% of “the world’s international boundaries” feels a little misleading…..the results show that 78% of EEZs will experience a shifting stock. The proportion of stocks is a much easier to understand figure (particularly in the abstract) an is more directly comparable to the 45% figure given in the next sentence. The 78% feels like an unnecessary attempt to be flashy in the abstract.

**Response:** Thank you, we have adopted the suggested approach. You will read in line 14 of page 1: "*Using global climate-fisheries model simulations, we show that 78% the world’s international boundaries will experience a shifting transboundary stock by 2030*".

- Pg 3, Line 2: First sentence doesn’t reflect the content in the rest of the paragraph. It would work better as a topic sentence for the third paragraph.

@@

- Pg 3, Line 7: change “have shifted” to “are shifting” – this paper shows the shifts aren’t done happening yet

@@

- Pg 4, Line 11-12: I don’t understand what is meant by “misalignment between fisheries resources allocation and distribution shifts” – language is confusing. Do the authors mean misalignment between fishing effort and stock biomass?

@@

- Pg 29: I realize the DBEM model is described in other papers, but a little more detail here would be helpful so that a reader doesn’t have to consult other papers to have a better sense of what the inputs are, how it was parameterized for each stock, etc. I suggest adding another paragraph to this effect.

@@

- Pg 30, lines 8-12: this text is repeated from earlier in the paragraph

@@

- Fig. S4 needs a color bar legend

>>>>

---
title: "Responses to Reviewer Three"
# output: pdf_document
output: word_document
---

@@

Informing global fisheries sustainability and meeting the SDG 2030 Agenda is a useful framing, in my opinion. However, given that framing and the research questions posed in this paper, I think the authors have overlooked two very important cases: 1) stocks that are currently confined to a single EEZ (“national stocks”) that will shift into transboundary stocks by 2100, and 2) stocks that are currently transboundary stocks that will shift entirel into a single EEZ by 2100, becoming national stocks. From a sustainability perspective, I am more concerned about case #1 than stocks that are already transboundary that are going to shift their distributions but maintain their transboundary status (the only cases currently examined in this paper). Some of those stocks might already have cooperative management agreements in place. And if they don’t, they are already plagued by the overharvesting that is likely to occur in the absence of international cooperation. Stocks that are currently national, however, have a higher likelihood of being managed sustainably now, and that likelihood will decline when they become transboundary. This seems like the most important case to analyze, and one that seems totally feasible to examine within the authors’ analysis framework, and yet this seems to have been completely overlooked. I also think it would be interesting to determine what proportion of current transboundary stocks become national stocks – the authors should have been able to detect these cases and I would assume there are some, but it is not mentioned anywhere in the paper. This seems like a missed opportunity for greater insights and is a mismatch between the stated goals of the paper and the results that are presented.

@@

Pg 9, Line 6: is 59% the proportion of stocks that will shift their catch distribution? Or is it the average proportion of the catch that shifts between countries?

@@

The methods are ENTIRELY in the supplementary materials. I have no problem with more abbreviated methods in the main paper and more details in the supplement, but there needs to be some methods in the main paper. A reader needs to be able to understand the basic approach without going to the supplementary materials.

@@

Pg 31-32: Does the TI capture the equality of sharing of the stock between two countries, or just how stable it is over time? The text claims an increasing TI means management is getting more challenging and a decreasing TI that the sharing between countries is becoming more stable (but not necessarily more equal)….is that the right interpretation? And how does that align with the example in Fig S6, where the TI seems to decline over the entire time series…..does that mean the sharing is becoming more stable?

- **Response:** Thank you for your comment. The transboundary index only captures the sharing stability over time. We had originally explored the directionality of the TI per stock, however, this was removed from the analysis as we rather focused on the "time of emergence" of the future TI from historical variability. Thus, since we do not talk about the directionallity of the TI (nor the TI *per se*) we have removed this sentence to avoid misunderstanding. Please note that the equality of sharing is measured by the Stock Share Ratio described under *Quantifying the intensity of transboundary stocks’ range shift.*

I like the time of emergence concept and how it was applied in this analysis.

- **Response:** We appreciate the acknowledgment on our methods.

I also like the idea of the threat point analysis to identify when a stock is sufficiently shared with another country to motivate cooperative management. However, I was confused by how the threat point was implemented using the stock share ratio (SSR) – why is the threat point determined relative to the historic SSR? I assume the idea of a threat point from game theory is based on the proportion of catch or value that is shared, and I don’t see how the starting point SSR would be relevant? Maybe I misunderstood what the authors did here, but conceptually/theoretically I’m not understanding the rationale for their approach so at the very least it needs more explanation and justification. But I’m concerned it actually needs to be based on a theoretical proportion, not a quantity interpreted relative to a historic proportion.

- **Response:** We have revised the text to clarify this point as we believe the reviewer misunderstood our approach. We ofer and explanation below, and inlcuded some more detailed in the methods of the main manuscript (see page *XXX*, line *XX*) and in the Supplemental Material (see page *XXX* line *XX*).

  The reviewer is correct to "*assume the idea of a threat point from game theory is based on the proportion of catch or value that is shared"* and that is exactly what we mean here with the stock share ratio (SSR). Here, the SSR represents the proportion of a transboundary stock's catch that each country has per year. We do realize we loosly used the concepts of SSR and catch proportion when they mean the same thing. This has been clarified in the text.

  If we think on two countries managing a transboundary stock from 1951 to 2000, we can assume that both countries are adapted to the historical stock share ratio. This is not a single value but a series of combinations (e.g., year 1 40/50, year 2 30/60, year 3 50/50... n). Since management continues over the historical time period, we can assume both countries are happy with the historic SSRs. However, as game theory states, for a cooperative strategy to work, the benefit a player gets (in this case the SSR) must not be less than the benefit under a non-cooperative strategy. While we could set the threat point as a theoretical proportion as suggested by the reviewer, but if we assume countries are collaborating, then the threat point can be the minimum historic SSR that each country had (in our case SSR $\pm$ 2 s.d for a more conservative scenario; see equation **X**). This assumes that no country will be willing to collaborate if the future catch proportion of the transboundary stock is lower than it has ever been. This method was previously applied by Palacios-Abrantes *et al.* (2020) and Sumaila *et al* (2020).

 - Palacios-Abrantes J, Sumaila UR, Cheung WWL. 2020. Challenges to transboundary fisheries management in North America under climate change. Ecology and Society 25:art41–17.

 - Sumaila UR, Palacios-Abrantes J, Cheung WWL. 2020. Climate change, shifting threat points, and the management of transboundary fish stocks. Ecology and Society 25:art40–9. The Resilience Alliance.

I think a version of Fig. S6 would be useful for the main paper. (But a few small comments about this figure: in panel a, I don’t understand why the EEZ centroids aren’t shown in the middle of the EEZ boxes? Also, for panel b, I see a red open circle in the legend, but I don’t see that anywhere on the actual figure.)

- **Response:** Thank you for noticing the misplace of the EEZ centroids. The figure has been corrected and included the figure in the main text (It is now Fig. 1). The open red circles are located in the bottom panel (B) in each time step where the future distribution overpasses the natural variability.

@@

I know this is nitpicky, but please don’t have line numbers restart on each page. It just makes it more cumbersome on a reviewer trying to give detailed comments.

- **Response:** We understand (and agree!) with this comment. Unfortunately, this is how the *Science* template was distributed to us.

Page1, Line 15: I suggest reporting the proportion of stocks (which looks like it would be between 20-25%), rather than the 78% reported here. Saying that transboundary stocks will shift their distributions across 78% of “the world’s international boundaries” feels a little misleading…..the results show that 78% of EEZs will experience a shifting stock. The proportion of stocks is a much easier to understand figure (particularly in the abstract) an is more directly comparable to the 45% figure given in the next sentence. The 78% feels like an unnecessary attempt to be flashy in the abstract.

- **Response:** Thank you, we have adopted the suggested approach. You will read in line 14 of page 1: "*Using global climate-fisheries model simulations, we show that 78% the world’s international boundaries will experience a shifting transboundary stock by 2030*".

Pg 3, Line 2: First sentence doesn’t reflect the content in the rest of the paragraph. It would work better as a topic sentence for the third paragraph.

@@

Pg 3, Line 7: change “have shifted” to “are shifting” – this paper shows the shifts aren’t done happening yet

@@

Pg 4, Line 11-12: I don’t understand what is meant by “misalignment between fisheries resources allocation and distribution shifts” – language is confusing. Do the authors mean misalignment between fishing effort and stock biomass?

@@

Pg 29: I realize the DBEM model is described in other papers, but a little more detail here would be helpful so that a reader doesn’t have to consult other papers to have a better sense of what the inputs are, how it was parameterized for each stock, etc. I suggest adding another paragraph to this effect.

@@

Pg 30, lines 8-12: this text is repeated from earlier in the paragraph

@@

Fig. S4 needs a color bar legend
